thesis2024

### 2025-03-24 thesis2024.tex
Appendices with individual numbering added
Yalm structure and base qmd created. To populate with the actual articles.

\chapter*{Preface}\label{preface}
\addcontentsline{toc}{chapter}{Preface}

\markboth{Preface}{Preface}

@@

@@

\chapter{Summary}\label{summary}

@@

@@

>>>>

\chapter*{Acknowledgments}\label{acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}

\markboth{Acknowledgments}{Acknowledgments}

@@

\chapter{Abstract}\label{abstract}

@@

\chapter{Creating frames of reference for chert exploitation during the
Late Pleistocene in Southwesternmost
Iberia}\label{creating-frames-of-reference-for-chert-exploitation-during-the-late-pleistocene-in-southwesternmost-iberia}

\chapter{Within and Beyond: Chert Procurement Patterns During The Upper
Palaeolithic in Southwesternmost
Iberia}\label{within-and-beyond-chert-procurement-patterns-during-the-upper-palaeolithic-in-southwesternmost-iberia}

@@

\chapter{From Stone to Tool}\label{from-stone-to-tool}

\chapter{Discussion and final
remarks}\label{discussion-and-final-remarks}

@@

\cleardoublepage
\phantomsection
\addcontentsline{toc}{part}{Appendices}
\appendix

\chapter{Supplementary materials 1}\label{supplementary-materials-1}

Some supplementary materials.
